Software Citation Principles

### 2016-07-25 sc-principles/software-citation-principles.tex
finishing up use case about publishing software

\niemnote{this seems the same as use case 1} \katznote{I thought it was the same as 6}
\niemnote{6 is about reproducing, while this seems to be writing a software paper} \katznote{ok, I guess this is like 1, but in 1, the research is using someone else's software, and here, the researcher is using their own software.  Maybe this doesn't matter so much.  So should we just add a comment that this is the same as 1 other than the fact that the software developer and paper author are mostly the same here?}
The research wants to publish about a version of software they have produced.
A key part of this use case is to be able to connect the given narrative to a specific version of the software in questions and connect that in large story.

@@

>>>>

The research wants to publish about a version of software they have produced.
A key part of this use case is to be able to connect the given narrative to a specific version of the software in questions and connect that in large story.

@@

This is similar to use case 1, other than the fact that the software developer(s) and
paper author(s) will likely be the same person\slash people here.
